BoostEM

### 2014-05-04 paper/paper.tex
some more push

\documentclass[letterpaper,12pt]{article}
% define the title
\usepackage{subfig}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{array}

\usepackage{epigraph}
\usepackage{url}

% \epigraphsize{\small}% Default
\setlength\epigraphwidth{16cm}
\setlength\epigraphrule{1pt}
\usepackage[margin=1in]{geometry}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\epigraph}{\@epitext{#1}}{\itshape\@epitext{#1}}{}{}
\makeatother\usepackage{algorithm}
\usepackage{multirow}
\usepackage{algpseudocode}
\begin{document}
% generates the title
\bibliographystyle{acm}

\begin{titlepage}
\begin{center}

% Upper part of the page. The $'$~$'$ is needed because \\
% only works if a paragraph has started.

\textsc{\huge Bad Commit Smells}\\[0.5cm]
\textsc{ Those Who Do Not Learn From Their Commit History Will be Doomed to Revert it}\\[1.0cm]

% Author and supervisor
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
Steven \textsc{Johnson}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
Zach \textsc{Welch}
\end{flushright}
\end{minipage}\\[1.5cm]

\large University of Wisconsin \textsc{Madison}\\[1.5cm]

\begin{abstract}
THIS SHOULD BE OUR ABSTRACT
\end{abstract}

\vfill

% Bottom of the page
{\large \today}

\end{center}
\end{titlepage}

% insert the table of contents
\tableofcontents
\listoffigures
\listoftables
\epigraph{Yeah Science!!}{ \textup{Jesse Pinkman}}

\section{Introduction}
\section{Related Work}
\section{Approach}

\bibliography{Master}

% that`s all folks
\end{document}

>>>>

% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{CS 760}{'14,Madison WI, USA}
\CopyrightYear{2014} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{BoostEM}
\subtitle{A Semi-Supervised Ensemble Method}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Zach Welch\\
       \affaddr{UW-Madison}\\
       \email{zwelch@cs.wisc.edu}
% 2nd. author
\alignauthor
Steven Johnson\\
       \affaddr{UW-Madison}\\
       \email{sjj@cs.wisc.edu}
}
\date{May 12, 2014}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
We introduce BoostEM, a semi-supervised learning algorithm which combines the benefits of using an ensemble method like Boosting with the benefits of using unlabeled data.  BoostEM is intended for use in learning settings with an abundance of unlabeled data, and outperforms the traditional AdaBoost algorithm and learning with fractional data from using Expectation Maximization across a variety of base learners and data sets.
\end{abstract}

% A category with the (minimum) three required fields
\section{Introduction}
STEVE
\section{Background}
\subsection{Boost}
\subsection{Expectation Maximization}
\section{Related Work}
\section{BoostEM}
\section{Evaluation}
\subsection{Methodology}
STEVE
\subsection{Results}
\section{Discussion}
STEVE 
\section{Conclusions}
%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}

\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case

\end{document}
